---
title: "Manual model development"
output: html_notebook
---

```{r}
# load libraries
library(tidyverse)
library(janitor)
library(GGally)
library(ggfortify)
library(modelr)

# load and explore data
house <- read_csv('../data/kc_house_data.csv')
names(house)
summary(house)
```
# 2 Question 1

Tidy up the data ready for regression.

```{r}
# turn `waterfront` and `renovated` into logical vectors and remove unnecessary columns
house_clean <- house %>% 
  mutate(waterfront = as.logical(waterfront), 
         renovated = as.logical(yr_renovated)) %>% 
  select(-id, -date, -sqft_living15, -sqft_lot15, -zipcode, -yr_renovated)
```

# 3 Question 2

Check for aliased variables using the alias() function (this takes in a formula object and a data set). [Hint - formula price ~ . says ‘price varying with all predictors’, this is a suitable input to alias()]. Remove variables that lead to an alias. Check the ‘Elements of multiple regression’ lesson for a dropdown containing further information on finding aliased variables in a dataset.

```{r}

alias(lm(price ~ ., data = house_clean)) # `sqft_basement` can be calculated from `sqft_living - sqft_above` so no need for it

house_trim <-  house_clean %>% # remove `sqft_basement` write new trimmed dataset ready to model
  select(-sqft_basement)

alias(lm(price ~ ., data = house_trim)) # final check for aliases

```

# 4 Question 3

Systematically build a regression model containing up to four main effects (remember, a main effect is just a single predictor with coefficient), testing the regression diagnostics as you go * splitting datasets into numeric and non-numeric columns might help ggpairs() run in manageable time, although you will need to add either a price or resid column to the non-numeric dataframe in order to see its correlations with the non-numeric predictors.

```{r}
house_trim_numeric <- house_trim %>%
  select_if(is.numeric)

house_trim_nonnumeric <- house_trim %>%
  select_if(function(x) !is.numeric(x))

house_trim_nonnumeric$price <- house_trim$price

ggpairs(house_trim)
ggpairs(house_trim_numeric)
ggpairs(house_trim_nonnumeric)
```
Interested in:

price ~ 

sqft_living,
sqft_above,
bathrooms,
waterfront,
grade,
view

## plot simple linear regression

```{r}
# start with simple linear regression
house_trim_numeric %>%
  ggplot(aes(x = sqft_living, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
## start model build

```{r}
model <- lm(price ~ sqft_living, data = house_trim_numeric)

autoplot(model)
summary(model)
```
r^2 = 0.4929
res = 261500

```{r}
model2 <- lm(price ~ sqft_living + grade, data = house_trim_numeric)

autoplot(model2)
summary(model2)
```

r^2 = 0.5345
res = 250500


```{r}
model3 <- lm(price ~ sqft_living + grade + bathrooms, data = house_trim_numeric)

autoplot(model3)
summary(model3)
```
r^2 = 0.5371
res = 249800


```{r}
model4 <- lm(price ~ sqft_living + grade + view, data = house_trim_numeric)

autoplot(model4)
summary(model4)
```

r^2 = 0.5725
res = 240000

```{r}
model_nn_1 <- lm(price ~ waterfront, data = house_trim_nonnumeric)

autoplot(model_nn_1)
summary(model_nn_1)
```

```{r}
model5 <- lm(price ~ sqft_living + grade + view + sqft_above, data = house_trim_numeric)

autoplot(model5)
summary(model5)
```

r^2 = 0.5744
res = 239500

```{r}
anova(model5)
```

