---
title: "Homework"
output: html_notebook
---

```{r}
library(tidyverse)
```
Question 1.
Find the weather forecast for the next three days online. Create a list of lists in which each inner list should be labelled with the name of the day of the week. Each inner list should contain named elements telling you the temperature, chance of rain and wind speed.
```{r}
weather_forecast <- list(
                "Thursday" = list(temperature = 8, chance_of_rain = 50, wind_speed = 15),
                "Friday" = list(temperature = 10, chance_of_rain = 75, wind_speed = 25),
                "Saturday" = list(temperature = 7, chance_of_rain = 20, wind_speed = 5)
)

weather_forecast
```

Question 2.
Using the list you’ve just made find:

The chance of rain tomorrow
The wind speed on the day after tomorrow
The temperature tomorrow.

```{r}

weather_forecast$Thursday$chance_of_rain
weather_forecast$Friday$wind_speed
weather_forecast$Thursday$temperature


```

Question 3.
Find a 14 day forecast online and create a matrix of the forecasts for temperature, where each week is one row and columns correspond to days.

You will want to give a name to the matrix you create.

```{r}

temps <- (c(11L, 13L, 15L, 12L, 11L, 13L, 12L, 12L, 12L, 12L, 12L, 12L, 12L, 12L))
# add `L` after numbers

forecast <- matrix(temps, nrow = 2, ncol = 7)

forecast

```

Question 4.
From the matrix you just made select:

The third day of the second week
The whole second week
The first, third and fifth days in both weeks.

```{r}
forecast[2,3]
forecast[2,1:7]
forecast[2, ] # or could use this for the same result above
forecast[ ,c(1, 3, 5)]

```

Question 5.
Write a function that pre-appends “The answer is:” to any character input, while for numeric input, it either just returns the number for numbers less than 10, or divides the number by 10 for numbers greater than 10. For anything else return “Invalid input”.

```{r}
# this was my attempt below. It worked but could have been cleaner and I missed on part of the second if function. Better code below mine.

# crazy_function <- function(i){
  
#   if (is.character(i)) {
#     return(
#       paste("The answer is:" ,i))
#   }
#     if (is.numeric(i) == TRUE) {
#       
#     if (i <= 10){
#       print(i)}
#    
#    if (i > 10){
#       print(i)}
#   } 
#     else{
#       print("Invalid input")
#     }
#   
# }
# crazy_function("bingo!")

# this is a better solution

crazy_function <- function(i){
  if (is.character(i)) {
    return(paste("The answer is:" ,i))
  }
  
  if (is.numeric(i)) {
    if (i < 10) {
      return(i)
    } else {
      return(i / 10)
    }
  } 
  
  return("Invalid input")
}


crazy_function(100)
  

```

Question 6.
Write a function which checks if two vectors have the same elements.

If they have the same elements in the same order, return “Exactly the same”
If they have the same elements but in a different order, return “The same”
If they don’t have the same elements, return “Different”.

```{r}
# assign matching or mismatching elements to these two vectors
one <- c(1,2,3) 
two <- c(3,2,1)

check_vector <- function(one, two){
  if (one == two){ # missing the `all` function here
    return(
      print("Exactly the same"))
  }
  if (one %in% two){ # need to use `sort` function here
    return(
      print("The same"))
  }
  if (one != two){ # don't need this code, just the return/print function at the end
    return( 
    print("Different"))
  }
}    

check_vector(one, two)

# this is working but throwing up warnings about condition length
# so I got this wrong, the `%in%` operator doesn't work for this example
# better code below

is_same_vector <- function(vector_1, vector_2) {
  if (all(vector_1 == vector_2)) {
    return("Exactly the same")
  }

  if (all(sort(vector_1) == sort(vector_2))) {
    return("The same")
  }

  return("Different")
}

a <- c(1, 2, 3, 4, 5)
b <- c(1, 4, 2, 3, 5)
c <- c(9, 4, 8, 1, 0)

is_same_vector(a, a)

```

```{r}
is_same_vector(a, b)

```

```{r}
is_same_vector(a, c)

```

