---
title: "Distributions homework"
author: "Jerry Balloch"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    number_sections: false
    df_print: paged
---

```{r include=FALSE}
# load in libraries
library(prob)
library(tidyverse)
library(janitor)
library(here)
```

# Question 1.
Load the data, clean_names() and explore it.
```{r}
# read in and clean data
phone_data <- read_csv(here('data/20190928-items.csv')) %>% 
  clean_names()

dim(phone_data)
names(phone_data)
head(phone_data)

```
# Question 2.
Find the brand with the highest numbers of phones in the dataset.

__Answer:__ Samsung has the highest number of phones in the dataset at 397.


```{r}
phone_data %>% 
  group_by(brand) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  head(1)
```
# Question 3.
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

__Answer:__ I think the histogram shows a relatively normal distribution, perhaps slightly left-skewed.

```{r}
phone_data_stats <- phone_data %>% 
  filter(brand == "Samsung") %>%
  summarise(mean_rating = mean(rating),
            sd_rating = sd(rating))

phone_data %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 25) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = phone_data_stats$mean_rating,
      sd = phone_data_stats$sd_rating
    ),
    col = "red"
  )
  
```

# Question 4.
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

__Answer:__ one sd = 79.3%, two sd = 91.9%, three sd = 97.9%   
Normal distribution should be 68% - 95% - 98.7% so we are close on two and three but over on one. 

```{r}
# get the z_score of the ratings column
phones_scaled <-  phone_data %>% 
  filter(brand == "Samsung") %>% 
  mutate(z_rating = scale(rating))

# calculate proportions of ratings within one standard deviation of the mean
count <- phones_scaled %>% 
  filter(between(z_rating, left = -1, right = 1)) %>% 
  nrow()

100 * count / nrow(phones_scaled)

# calculate proportions of ratings within two standard deviation of the mean
count <- phones_scaled %>% 
  filter(between(z_rating, left = -2, right = 2)) %>% 
  nrow()

100 * count / nrow(phones_scaled)

# calculate proportions of ratings within three standard deviation of the mean
count <- phones_scaled %>% 
  filter(between(z_rating, left = -3, right = 3)) %>% 
  nrow()

100 * count / nrow(phones_scaled)


```

```{r}

```

