---
title: "Model Building Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(modelr)
library(GGally)
library(ggfortify)
library(here)
library(lubridate)
```

```{r}
avocado <- read_csv(here('data/avocado.csv')) %>% 
  clean_names()

names(avocado)
dim(avocado)
head(avocado)
```

```{r}
# clean up data
# create `month` column from `date` and make it a `factor`
# make `type` a `factor`
# rename plu columns to make more sense
# remove un-needed columns

avocado_clean <- avocado %>% 
  mutate(month = as.factor(month(date)),
         type = as.factor(type)) %>% 
  rename(total_plu_4046 = x4046,
         total_plu_4225 = x4225,
         total_plu_4770 = x4770) %>% 
  select(-c(x1, date))

avocado_clean

avocado_trim <- avocado_clean %>% 
  select(-region)
```
```{r}
# check for any aliased variables
alias(average_price ~ ., data = avocado_clean)
```

```{r}
# plot `average_price` to see how it looks
ggplot(avocado_clean, aes(average_price)) + 
  geom_histogram(colour = "white")

ggplot(avocado_clean, aes(x = type, y = average_price)) +
  geom_boxplot()

ggplot(avocado_clean, aes(x = month, y = average_price)) +
  geom_boxplot()

ggplot(avocado_clean, aes(x = region, y = average_price)) +
  geom_boxplot()

```
- The `average_price` data looks to be pretty normally distributed.
- The `type` boxplot show a clear difference between the two types so this could be a good predictor to use.
- The `month` boxplot show variance throughout the year which could also affect price.
- The `region` boxplot show variance throughout regions which could also affect price.



```{r}
# run `ggpairs()` and look for interesting variables
# region is causing problems so remove it for the moment
avocado_clean %>% 
  select(-region) %>% 
  ggpairs()
```
### Interesting predictors

average_price ~
type, 
month,


```{r}
# create first model
mod1a <- lm(average_price ~ type, data = avocado_clean)
summary(mod1a)
```
`average_price ~ type` looks to be a good starting point for the model: Adjusted R-squared:  0.3792


```{r}
# create second model
mod1b <- lm(average_price ~ month, data = avocado_clean)
summary(mod1b)
```

`month` does look to affect the price but is not as good a starting point so will save to use as an added predictor to the model: Adjusted R-squared:  0.05953

```{r}
# create third model
mod1c <- lm(average_price ~ region, data = avocado_clean)
summary(mod1c)
```
`region` has more of an effect that `month` so will save to use as an added predictor too. Adjusted R-squared:  0.1657


```{r}
anova(mod1b, mod1c)

null_model <- lm(average_price ~ 1, data = avocado_clean)
anova(null_model, mod1c)
```
Using `anova` Model 2: average_price ~ region seems to be more significant


```{r}
autoplot(mod1a)
```
Plotting mod1a to have a look at residuals. Charts look okay.


```{r}
# adding residuals
avo_resid <- avocado_clean %>%
  add_residuals(mod1a) %>%
  select(-c("average_price", "type"))

avo_resid %>% 
  select(-region) %>% 
  ggpairs()
```

```{r}
# adding region to first model
mod2a <- lm(average_price ~ type + region, data = avocado_clean)
summary(mod2a)
```
Adding in `region` predictor has a decent impact, Adjusted R-squared:  0.546, up from 0.3792. No much of a penalty between r values yet either.



```{r}
# adding month as another predictor
mod2b <- lm(average_price ~ type + region + month, data = avocado_clean)
summary(mod2b)
```
Adding in `month` has a further good impact: Multiple R-squared:  0.6074,	Adjusted R-squared:  0.606,
still not being penalised much for the addition.


```{r}
# add interaction between `type:region`
mod3a <- lm(average_price ~ type + region + month + type:region, data = avocado_clean)
summary(mod3a)
```

Adding an interaction between `type:region`  gets us further, Multiple R-squared:  0.6472,	Adjusted R-squared:  0.6449, penalties still looking lean.



```{r}
# try a different interaction `type:month`
mod3b <- lm(average_price ~ type + region + month + type:month, data = avocado_clean)
summary(mod3b)
```

Not a strong a result here, mod3a much stronger.

----

# Trying automated model builder

Using `leaps` package, disregarding the `region` predictor

```{r}
library(leaps)
```

```{r}
regsubsets_forward <- regsubsets(average_price ~ ., 
                                 data = avocado_trim, 
                                 nvmax = 10, 
                                 method = "forward")
```

```{r}
sum_regsubsets_forward <- summary(regsubsets_forward)
sum_regsubsets_forward
```

```{r}
plot(regsubsets_forward, scale = "adjr2")
```
```{r}
plot(regsubsets_forward, scale = "bic")

```

```{r}
plot(sum_regsubsets_forward$rsq, type = "b")

```
Automated building seems to suggest that I was right in my manual building process to be selecting average_price ~ type, month, year as they all seemed to be the most significant predictors here, getting to a r2 of around 0.47. Adding in the region predictor would obvioulsy bring this up closer to where I got to building the model manually.

----

# tidy models

Having a quick look at the `tidymodels` package.

```{r}
library(tidymodels)
library(dotwhisker)
```

```{r}
ggplot(avocado_clean,
       aes(x = month, 
           y = average_price, 
           group = type, 
           col = type)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE) +
  scale_color_viridis_d(option = "plasma", end = .7) +
  facet_grid(~type)
```
```{r}
lm_mod <- linear_reg()

lm_fit <- lm_mod %>% 
  fit(average_price ~ type + region + month, data = avocado_clean)

lm_fit
```
```{r}
tidy(lm_fit)
```
```{r}
tidy(lm_fit) %>% 
  dwplot(dot_args = list(size = 2, color = "black"),
         whisker_args = list(color = "black"),
         vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2))