---
title: "Clustering Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(here)
library(factoextra)
library(broom)
```

# EDA

Mall data is a dataframe with 5 columns and 200 rows. All Columns are `double` apart from gender which is `character`, will probably change to factor or logical. No NA's are present in the data. the Columns are:

1. customer_id 
2. gender
3. age
4. annual_income_k
5. spending_score_1_100 - presumming score is from 1 to 100.

Max annual income appears to be 137k, max spending score is 99.

```{r}
# read in data and explore

mall <- read_csv(here('data/mall_customers.csv')) %>% 
  clean_names()

head(mall)
glimpse(mall)
```

```{r}
mall %>% 
  summarise(across(everything(), .fns = ~sum(is.na(.x))))

slice_max(mall, annual_income_k)
slice_max(mall, spending_score_1_100)

```


```{r}
# selecting columns to cluster
mall_trim <- mall %>% 
  select(-age, -gender)
mall_trim
```
```{r}
# quick plot to see how the data looks
ggplot(mall_trim, aes(x = annual_income_k, y = spending_score_1_100)) +
  geom_point()
```

```{r}
# scaling data
mall_scale <- mall_trim %>% 
  select(-customer_id) %>% 
  mutate(across(1:2, scale))
mall_scale


mall_scale %>% 
  as_tibble() %>% 
  pivot_longer(cols = c(annual_income_k, spending_score_1_100),
               names_to = "type",
               values_to = "value") %>% 
  group_by(type) %>% 
  summarise(mean = round(mean(value)),
            sd = sd(value))
```

```{r}
# check the plot after scaling, looks the same
ggplot(mall_scale, aes(x = annual_income_k, y = spending_score_1_100)) +
  geom_point()
```

# Clustering

Try a few methods to see how the data clusters. Looks like five cluster groups is a good way forward.

```{r}
# Elbow method
fviz_nbclust(mall_scale, 
             kmeans, 
             method = "wss", 
             nstart = 25)
```

```{r}
# silhouette method
fviz_nbclust(mall_scale, 
             kmeans, 
             method = "silhouette", 
             nstart = 25)
```

```{r}
# gap_stat method, not sure how to interpret this!
fviz_nbclust(mall_scale, 
             kmeans, 
             method = "gap_stat") 
```
## Set up clustering

```{r}
# kmeans to set up 5 clusters
clustered_mall_scale <- kmeans(mall_scale, 5, nstart = 25)

clustered_mall <- kmeans(mall_trim, 5, nstart = 25)
```

```{r}
# cluster sizes
clustered_mall_scale$size
```

```{r}
# cluster centres
clustered_mall_scale$centers

```

## Visualise the clusters

```{r}
clusters <- augment(clustered_mall_scale, mall_scale)

ggplot(clusters, aes(annual_income_k, spending_score_1_100, colour = .cluster)) +
  geom_point() 
```
```{r}
# plotting non scaled data
clusters_non_scaled <- augment(clustered_mall, mall_trim)

ggplot(clusters, aes(annual_income_k, spending_score_1_100, colour = .cluster)) +
  geom_point() 
```
Non scaled data changes the clusters slightly, but is easier to interpret.


```{r}
# looking at averages of income and spending score by cluster
clusters_non_scaled %>% 
  group_by(.cluster) %>%
  summarise(annual_income_k = mean(annual_income_k), spending_score_1_100 = mean(spending_score_1_100)) %>% 
  arrange(desc(spending_score_1_100))

```

# Comments on clusters and Targeting

After initial exploration I settled on building 5 clusters with the data. Once K-means clustering was completed we are left with 5 clusters as summarised above. The results are interesting from a targeting point of view. 

The two highest average earners, clusters 3 and 4, are separated by under 2k in earnings but the spending scores are very different, with the cluster that earns slightly less (4) scoring significantly higher. Cluster 4 actually has the highest average spending score (82) in the dataset. I would suggest targeting this cluster in the first instance.

As a second target group I would go with cluster 5 which although having the second lowest average income, has the second highest spending score (66).

Overall in terms of targeting based on spending score I would go for the following order: 4, 5, 2, 1, 3.