---
title: "Diamonds Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
library(GGally)
library(janitor)
library(modelr)
library(ggfortify)
```

# 1.

Load the `housing_prices.csv` data set and undertake an initial exploration of the data. You will find details on the data set on the relevant Kaggle page.

```{r}
housing_prices <- read_csv(here('data/housing_prices.csv'))

```

# 2. 

We expect the total_rooms of houses to be strongly correlated with total_bedrooms. Use `ggpairs()` to investigate correlations between these two variables.
```{r}
# checking correlation using ggpairs
ggpairs(housing_prices, columns = 4:5)

```
# 3.

So, we do find significant correlations. Let’s drop `total_bedrooms` from the dataset, and use only `total_rooms` going forward.

```{r}
# drop total_bedrooms column
housing_prices_no_beds <- housing_prices %>% 
  select(-total_bedrooms)

housing_prices_no_beds
```

# 4.

We are interested in developing a regression model for the `median_house_value` of a house in terms of the possible predictor variables in the dataset.

i. Use `ggpairs()` to investigate correlations between `median_house_value` and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r}
ggpairs(housing_prices_no_beds)

```

ii. Perform further ggplot visualisations of any significant correlations you find.

```{r}
housing_prices_no_beds %>% 
  ggplot(aes(total_rooms, households)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)

housing_prices_no_beds %>% 
  ggplot(aes(housing_median_age, median_house_value)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)

housing_prices_no_beds %>% 
  ggplot(aes(households, population)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)

housing_prices_no_beds %>% 
  ggplot(aes(median_income, median_house_value)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)

housing_prices_no_beds %>% 
  ggplot(aes(total_rooms, population)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)
```

iii. Shortly we may try a regression model to fit the categorical predictor ocean_proximity. Investigate the level of ocean_proximity predictors. How many dummy variables do you expect to get from it?

```{r}
housing_prices_no_beds %>% 
  add_predictions(model)
```

# 6.

Start with simple linear regression. Regress `median_house_value` on `median_income` and check the regression diagnostics.

```{r}
model <- lm(formula = median_house_value ~ median_income, data = housing_prices_no_beds)
summary(model)

autoplot(model)

```

# 7.

Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.

```{r}
model2 <- lm(formula = median_house_value ~ median_income:housing_median_age, data = housing_prices_no_beds)
summary(model2)

autoplot(model2)
```

