---
title: "Advanced ggplot2 Homework"
author: "Jerry Balloch"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    number_sections: false
    df_print: paged
---

```{r include=FALSE}

library(tidyverse)
library(here)
library(CodeClanData)

# load in data

qb_revenue_breakdown
qb_monthly_sales
qb_competitors
qb_device_data

```

# Question 1.
Take the data in the dataset `qb_revenue_breakdown` and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
ggplot(qb_revenue_breakdown) +
  aes(x = Product, y = Revenue, fill = Year) +
  geom_bar(position = "stack", stat = "identity")
```

# Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside `qb_monthly_sales`, but you will need to use `filter()` or `subset()` `(base R)`.

```{r}
ggplot(qb_monthly_sales %>% filter(Cashflow == "Kwikbit Unit 1 Sales")) +
  aes(x = Date, y = Amount) +
  geom_line() +
  labs(x = "Timeframe", 
       y = "Monthly Sales",
       title = "KwikBit Unit 1 Sales")
```

# Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in `qb_monthly_sales`.

```{r}
ggplot(qb_monthly_sales) +
  geom_line(aes(x = Date, y = Amount, colour = "Kwikbit Unit 1 Sales"),
            data = qb_monthly_sales %>% filter(Cashflow == "Kwikbit Unit 1 Sales")) +
  geom_line(aes(x = Date, y = Amount, colour = "Cost"),
            data = qb_monthly_sales %>% filter(Cashflow == "Cost"))
  

```

# Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use `geom_area`). This data is in `qb_competitors`.

```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, fill = Company) +
  geom_area()

```

# Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, colour = Company) +
  geom_line() +
  geom_point()
```

# Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in `qb_device_data`.

```{r}
ggplot(qb_device_data) +
  aes(x = hours, y = counts, colour = device) +
  geom_line() +
  facet_grid(id~device)
```

# Extension
Take the plots that you produced in part one and now polish them by:

Adding appropriate labels
Applying a unified theme, which is described below:
Graphs should have white backgrounds, and use colour sparingly.
There should be faint grid lines.
Font sizes should be ~12pt although titles should be slightly larger and axis labels can be slightly smaller.
All plots should use colours from the following company colour scheme.

```{r}

ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, colour = Company) +
  geom_line() +
  geom_point()+
  theme_minimal() +
  labs(
    title = "Competitor Sales",
    x = "Year",
    y = "Revenue"
  ) +
  theme(
    panel.background = element_rect(fill = "#FFFFFF"),
    panel.grid = element_line(),
    axis.text = element_text(size = 9),
    axis.title = element_text(size = 12),
    plot.title = element_text(size = 14)
  )
```

