---
title: "Weekend Homework - week 1"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(CodeClanData)
library(hrbrthemes)
library(viridis)

books <- read_csv('data/books.csv')

view(books)
names(books)
```

```{r}
spec(books)

head(books)
tail(books)
```


# Arranging by number of books per publisher


```{r}
# Arrange by number of books by publisher

books_by_publisher <- books %>% 
  group_by(publisher) %>% 
  summarise(
    number_books = n()) %>% 
  arrange(desc(number_books))

books_by_publisher

# created a 'top 20' list for using later on

books_by_publisher_20 <- books %>% 
  group_by(publisher) %>% 
  summarise(
    number_books = n()) %>% 
  arrange(desc(number_books)) %>% 
  head(20)

books_by_publisher_20


```
# Arranging by number of books per author

```{r}
# Arrange by number of books by author

books_by_author <- books %>% 
  group_by(authors) %>% 
  summarise(
    number_books = n()) %>% 
  arrange(desc(number_books))

books_by_author
```
# Average rating of all books

```{r}

# Average rating of books

books %>% 
  select(average_rating) %>% 
  summarise(mean(average_rating))

books %>% 
  select(average_rating) %>% 
  summarise(number_books = n(),
            avg_rating = round(mean(average_rating), digits = 1),
  ) 
  

```
# Arranging by number of books per publisher with average rating

```{r}
books_by_author_rated <- books %>% 
  group_by(authors) %>% 
  summarise(
    avg_rating = round(mean(average_rating), digits = 1),
    number_books = n())%>% 
  arrange(desc(number_books))

books_by_author_rated
```
# List of selected author's top 5 rated books

```{r}
books %>% 
  select(authors, title, average_rating, publisher) %>% 
  filter(authors == "P.G. Wodehouse") %>% 
  arrange(desc(average_rating)) %>% 
  head(5)

```
# Top 5 most read Authors and books - with average rating of book

```{r}
# Top 5 authors by number of ratings also showing average rating

most_rated_authors <- books %>% 
  select(authors, title, ratings_count, average_rating) %>% 
  arrange(desc(ratings_count)) %>% 
  head(5)

most_rated_authors

```

# Finding out the number of books by language

```{r}
# Arrange by number of books by language

books_by_language <- books %>% 
  group_by(language_code) %>% 
  summarise(
    number_books = n()) %>% 
  arrange(desc(number_books))

books_by_language
```



# Graph of Top 20 publishers by volume of books published

Code from the 'Coding for Data Analysis Workshop' I did before I started this course.


```{r}

plot_books_by_publisher <- books_by_publisher_20 %>%
  ggplot(aes(x = reorder(publisher, desc(number_books)), y = number_books)) +
  geom_col(fill = "orange") + 
  theme_light() +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  scale_y_continuous(expand = c(0,0)) +
  xlab("Publisher") + 
  ylab("Books published")


plot_books_by_publisher

```
# Mucking about with ggplot Bubble Chart

Not really working but fun to give it a bash.
Bubble size is average rating of Author.
```{r}

install.packages("viridis")
install.packages("hrbrthemes")

library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(viridis)


books_by_author_rated_20 %>%
  arrange(desc(avg_rating)) %>%
  mutate(authors = factor(authors, authors)) %>%
  ggplot(aes(x=authors, y=number_books, size = avg_rating, color=authors)) +
  geom_point(alpha=0.5) +
  scale_size(range = c(.1, 15), name="Rating") +
  scale_fill_viridis(discrete=TRUE, guide=FALSE, option="A") +
  theme_ipsum() +
  theme(legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  ylab("Number of Books") +
  xlab("Author") +
  theme(legend.position = "none")





```



```{r}
# Trying to filter out rows that contain collections or 
# more than one book by page count but not enough data

#books %>% 
#select(num_pages, title) %>% 
#  arrange(desc(num_pages))



```



