---
title: "Text Mining Homework"
author: "Jerry Balloch"
output: html_notebook
---

```{r message=FALSE}
library(tidyverse)
library(tidytext)
library(janeaustenr)
library(textdata)
library(ggwordcloud)
```

# MVP

## 1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.

```{r}
book_pride <- tibble(
  text = prideprejudice,
  sentence = 1:length(prideprejudice)) %>% 
  unnest_tokens(word, text)

book_sense <- tibble(
  text = sensesensibility,
  sentence = 1:length(sensesensibility)) %>% 
  unnest_tokens(word, text)

# most common words in Pride & Prejudice
book_pride %>% 
  count(word, sort = TRUE)  %>%
  head(10)
```
```{r}
# most common words in Sense & Sensibility
book_sense %>% 
  count(word, sort = TRUE) %>% 
  head(10)
```

## 2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.

```{r}
# remove stop words
book_pride_no_stop <- tibble(
  text = prideprejudice,
  sentence = 1:length(prideprejudice)) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words, by = "word") 

book_sense_no_stop <- tibble(
  text = sensesensibility,
  sentence = 1:length(sensesensibility)) %>% 
  unnest_tokens(word, text) %>% 
  anti_join(stop_words, by = "word")

# most common words in Pride & Prejudice
book_pride_no_stop %>% 
  count(word, sort = TRUE)
```
```{r}
# most common words in Sense & Sensibility
book_sense_no_stop %>% 
  count(word, sort = TRUE) 
```


## 3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

```{r}
# Pride and Prejudice
pride_sentiments <- book_pride_no_stop %>% 
  inner_join(get_sentiments("bing"), by = "word")

# Positive sentiments
pride_sentiments %>% 
  filter(sentiment == "positive") %>% 
  count(word, sort = TRUE) %>% 
  head(5)

# Negative sentiments
pride_sentiments %>% 
  filter(word != "miss") %>% 
  filter(sentiment == "negative") %>% 
  count(word, sort = TRUE) %>% 
  head(5)

# Sense & Sensibility
sense_sentiments <- book_sense_no_stop %>% 
  inner_join(get_sentiments("bing"), by = "word")

# Positive sentiments
sense_sentiments %>% 
  filter(sentiment == "positive") %>% 
  count(word, sort = TRUE) %>% 
  head(5)

# Negative sentiments
sense_sentiments %>% 
  filter(word != "miss") %>% 
  filter(sentiment == "negative") %>% 
  count(word, sort = TRUE) %>% 
  head(5)
```
### Wordcloud of each book

```{r message=FALSE}
pop_pride_ns <- book_pride_no_stop %>% 
  count(word, sort = TRUE)

# word cloud of Pride and Prejudice
ggwordcloud(pop_pride_ns$word, 
            pop_pride_ns$n, 
            random.order = FALSE, random.color = FALSE, 
            colors = pop_pride_ns$n,
            ordered.colors = TRUE)
```

```{r message=FALSE}
pop_sense_ns <- book_sense_no_stop %>% 
  count(word, sort = TRUE) 

# word cloud of Sense and Sensibility
ggwordcloud(pop_sense_ns$word, 
            pop_sense_ns$n, 
            random.order = FALSE, random.color = FALSE, 
            colors = pop_sense_ns$n, 
            ordered.colors = TRUE)
```

# Extension

### Visualise the sentiment of 'Pride and Prejudice' against 'Sense and Sensibility'

```{r}
# Get sentiment scores using `afinn` lexicon
pride_sentiment_scores <- book_pride_no_stop %>% 
  inner_join(get_sentiments("afinn"), by = "word")

sense_sentiment_scores <- book_sense_no_stop %>% 
  inner_join(get_sentiments("afinn"), by = "word")

```

```{r}
# calculate the mean and total sentiments
pride_sentence_sentiments <- pride_sentiment_scores %>% 
  group_by(sentence) %>% 
  summarise(n_words = n(),
            mean_sentiment = mean(value),
            total_sentiment = sum(value))

pride_sentence_sentiments

sense_sentence_sentiments <- sense_sentiment_scores %>% 
  group_by(sentence) %>% 
  summarise(n_words = n(),
            mean_sentiment = mean(value),
            total_sentiment = sum(value))

sense_sentence_sentiments
```


```{r}
# plot the sentiments of both books using the means
ggplot(pride_sentence_sentiments, aes(sentence, mean_sentiment)) +
  geom_smooth(method = "loess", colour = "pink", se = FALSE) +
  geom_smooth(data = sense_sentence_sentiments, 
              aes(sentence, mean_sentiment), method = "loess", colour = "purple", se = FALSE) +
  labs(title = "Sentiment of Pride and Prejudice (pink) vs Sense and Sensibility (purple)") +
  theme_minimal()

```


