---
title: "R Notebook"
output: html_notebook
---

```{r}
library(shiny)
library(tidyverse)
library(shinythemes)
library(janitor)
library(here)
library(lubridate)

workout_data <- read_csv(here::here("data/Workouts-2022-01-01-2022-04-01.csv"))
health_data <- read_csv(here::here("data/HealthAutoExport-2022-01-01-2022-04-01 Data.csv"))
workout_data_filtered <- read_csv(here::here("data/workout_data.csv"))

workout_data <- clean_names(workout_data)
health_data <- clean_names(health_data)
```


```{r}
```{r}
health_data %>% 
  ggplot() +
  aes(x = date, y = heart_rate_max_count_min, colour = "Max HR") +
  geom_path() +
  geom_point(aes(y = resting_heart_rate_count_min, colour = "resting HR")) +
  geom_point(aes(y = blood_oxygen_saturation_percent, colour = "Blood Oxygen %"))
```

```{r}
health_data %>% 
  group_by(date) %>% 
  ggplot() +
  aes(x = date, y = step_count_count) +
  geom_col() +
  geom_line(aes(y = basal_energy_burned_k_j, colour = "energy"))

```

```{r}

#making a month column

health_data <- health_data %>% 
  mutate(month = months(date), .before = 1)

workout_data <- workout_data %>% 
    mutate(month = months(start), .before = 1) %>% 
    mutate(date = date(start), .before = 2)
  


```

```{r}
health_data %>% 
  na.omit(step_count_count) %>% 
  sum(health_data$step_count_count)
```

