---
title: "Simple Linear Regression Homework"
output: html_notebook
---

```{r include=FALSE}
library(tidyverse)
library(modelr)
library(here)
library(janitor)
library(broom)
library(ggfortify)

project_management <- read_csv(here('data/project_management.csv'))

project_management

```

### Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.

The plot shows positive correlation.

```{r}
project_management %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE)
```

### Calculate the correlation coefficient of estimated_length and actual_length and interpret the value you obtain.

__answer__
The correlation coefficient is 0.80 which means on the JD Evans Magnitude scale it is very strongly positively correlated.

```{r}

cor(project_management$estimated_length, project_management$actual_length)

```

### Perform a simple linear regression using actual_length as the dependent variable, and estimated_length as the independent variable. Save the model object to a variable.

```{r}
model <- lm(actual_length ~ estimated_length,
            data = project_management)

summary(model)
```

### Interpret the regression coefficient of estimated_length (i.e. slope, gradient) you obtain from the model. How do you interpret the r2 value reported by the model?

__answer__
The p-value scores three stars (***) meaning it is statistically significant. The Adjusted R-squared value is 0.6401

### Is the relationship statistically significant? Remember, to assess this you need to check the p-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the p-value will be reliable (don’t worry about any outlier points you see in the diagnostic plots, we’ll return to them in the extension).

__answer__
According to the regression diagnostic plots below, the p-value looks to be reliable. The trend line on the Residuals vs Fitted plot looks to stay fairly close to 0 so in this case we can assume the p-value is reliable. If you look at the Q-Q graph the points sit on the line on the whole with the exception of a few outliers.

```{r}
autoplot(model)

```

